---
title: "Fray Jorge Bryophyte Metacommunities"
author: "Matthew Chmielewski"
date: "February 16, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

load packages
```{r}
library("tidyverse", "metacom", "ggrepel", "stringr")

```

load data
```{r}
pnfj<-read.csv(file = "group_meansfinal.csv", row.names = 1 )
head(pnfj)
length(subset(pnfj$site, pnfj$patch == "A"))

```

plot abundance of species by site
```{r}
plot(A~site, data= pnfj)
plot(B~site, data= pnfj)
plot(C~site, data= pnfj)
plot(D~site, data= pnfj)
plot(E~site, data= pnfj)
plot(F~site, data= pnfj)
plot(G~site, data= pnfj)
plot(H~site, data= pnfj)
plot(I~site, data= pnfj)
plot(J~site, data= pnfj)
plot(K~site, data= pnfj)
plot(L~site, data= pnfj)
plot(M~site, data= pnfj)
plot(N~site, data= pnfj)
plot(P~site, data= pnfj)

```


alter abundance to binary data
```{r}
binarypnfj<-!is.na(pnfj)
binarypnfj2<-binarypnfj*1
binarydf<-as.data.frame(binarypnfj2)
binarydf$site<-pnfj$site
binarydf$patch<-pnfj$patch
binarydf$height<-pnfj$height
head(binarydf)
```

split data into subsets of interest
```{r}
binaryhigh<-subset(binarydf, binarydf$height == "H")
binarylow<-subset(binarydf, binarydf$height == "L")
binaryA<-subset(binarydf, binarydf$patch == "A")
binaryB<-subset(binarydf, binarydf$patch == "B")
binaryC<-subset(binarydf, binarydf$patch == "C")
binaryD<-subset(binarydf, binarydf$patch == "D")
binaryE<-subset(binarydf, binarydf$patch == "E")
binaryF<-subset(binarydf, binarydf$patch == "F")
binaryG<-subset(binarydf, binarydf$patch == "G")
binaryH<-subset(binarydf, binarydf$patch == "H")
binaryI<-subset(binarydf, binarydf$patch == "I")
binaryJ<-subset(binarydf, binarydf$patch == "J")
binaryK<-subset(binarydf, binarydf$patch == "K")
binaryL<-subset(binarydf, binarydf$patch == "L")
binaryM<-subset(binarydf, binarydf$patch == "M")
binaryN<-subset(binarydf, binarydf$patch == "N")
binaryO<-subset(binarydf, binarydf$patch == "O")
binaryP<-subset(binarydf, binarydf$patch == "P")	
binaryQ<-subset(binarydf, binarydf$patch == "Q")
binaryR<-subset(binarydf, binarydf$patch == "R")
binaryS<-subset(binarydf, binarydf$patch == "S")
binaryT<-subset(binarydf, binarydf$patch == "T")

```

Listing columns that are missing values for metacom analysis
```{r}
subsetnames<- c("high", "low", "A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", "N", "O", "P", "Q", "R", "S", "T")


binarylist<-list(binaryhigh[,c(-1,-17,-18)], binarylow[,c(-1,-17,-18)], binaryA[,c(-1,-17,-18)], binaryB[,c(-1,-17,-18)], binaryC[,c(-1,-17,-18)], binaryD[,c(-1,-17,-18)], binaryE[,c(-1,-17,-18)], binaryF[,c(-1,-17,-18)], binaryG[,c(-1,-17,-18)], binaryH[,c(-1,-17,-18)], binaryI[,c(-1,-17,-18)], binaryJ[,c(-1,-17,-18)], binaryK[,c(-1,-17,-18)], binaryL[,c(-1,-17,-18)], binaryM[,c(-1,-17,-18)], binaryN[,c(-1,-17,-18)], binaryO[,c(-1,-17,-18)], binaryP[,c(-1,-17,-18)], binaryQ[,c(-1,-17,-18)], binaryR[,c(-1,-17,-18)], binaryS[,c(-1,-17,-18)], binaryT[,c(-1,-17,-18)])

dropvalues<-lapply(binarylist, colSums)
names(dropvalues) <- subsetnames
dropvalues
```

determine metacommunity structure: must remove any species with zero observations for each subset of interest
```{r}

testlist<-list(binaryhigh[,c(-1,-16,-17,-18)], binarylow[,c(-1,-17,-18)])

newlist<-list(binaryhigh[,c(-1,-16:-18)], binarylow[,c(-1, -17, -18)], binaryA[,c(-1,-13:-18)], binaryB[,c(-1,-12:-18)], binaryC[,c(-1, -3, -13:-18)], binaryD[,c(-1, -9, -13:-18)], binaryE[,c(-1:-3, -6, -9, -13, -16:-18)], binaryF[,c(-1:-4, -6, -8, -9, -12, -14:-18)], binaryG[,c(-1, -3, -6, -8, -9, -13,-15:-18)], binaryH[,c(-1:-3, -6, -16:-18)], binaryI[,c(-1, -3, -6, -8, -9, -12, -16:-18)], binaryJ[,c(-1,-6, -8, -9, -11, -16:-18)], binaryK[,c(-1, -6, -8, -9, -12, -13, -16:-18)], binaryL[,c(-1,-4, -6, -8, -9, -13, -16:-18)], binaryM[,c(-1, -3, -6, -8, -9, -13, -16:-18)], binaryN[,c(-1:-4, -6, -8, -9, -12:-18)], binaryO[,c(-1, -6, -8, -9, -13, -14, -16:-18)], binaryP[,c(-1, -6, -8, -9, -17,-18)], binaryQ[,c(-1, -3, -4, -6, -8, -9, -14, -16:-18)], binaryR[,c(-1, -3, -6, -8, -9, -13, -16:-18)], binaryS[,c(-1, -3, -4, -6, -8, -9, -16:-18)], binaryT[,c(-1, -3, -6, -9, -11, -16:-18)])

wholepark<-metacom::Metacommunity(binarydf[, c(-1, -17, -18)])
binarydf
bryo_metacommunities<-lapply(newlist, metacom::Metacommunity)
names(bryo_metacommunities) <- subsetnames
# can now call individual outputs as well as output features in the below object
bryo_metacommunities


test1<-metacom::Metacommunity(binarylow[, c(-1, -17, -18)], method = "swap")
test2<-metacom::Metacommunity(binarylow[, c(-1, -17, -18)])

saveRDS(bryo_metacommunities, "bryometa")

#visualize all ordinated matrices below

#whole park
metacom::Imagine(binarydf[, c(-1, -17, -18)], col = c(0, 1), order = FALSE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = rownames(binarydf[, c(-1, -17, -18)]), speciesnames = colnames(binarydf[, c(-1, -17, -18)]),
  binary = TRUE)

#subsets
lapply(newlist, metacom::Imagine, col = c(0, 1), order = TRUE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,binary = TRUE)

#plot them
pdf("plots/ordinatedmatrixes.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(metacom::Imagine(binarydf[, c(-1, -17, -18)], col = c(0, 1), order = FALSE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = "", speciesnames = colnames(binarydf[, c(-1, -17, -18)]),
  binary = TRUE))
plot(lapply(newlist, metacom::Imagine, col = c(0, 1), order = TRUE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", sitenames = "", yline = 2, xline = 2,binary = TRUE))
dev.off()

metacom::Imagine(binarydf[, c(-1, -17, -18)], col = c(0, 1), order = FALSE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = rownames(binarydf[, c(-1, -17, -18)]), speciesnames = colnames(binarydf[, c(-1, -17, -18)]),
  binary = TRUE)


metacom::Imagine(binaryhigh[,c(-1, -16, -17,-18)], col = c(0, 1), order = FALSE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = rownames(binaryhigh[,c(-1, -16, -17,-18)]), speciesnames = colnames(binaryhigh[,c(-1, -16, -17,-18)]),
  binary = TRUE)

metacom::Imagine(binarypnfj2[,c(-1,-17,-18)], col = c(0, 1), order = TRUE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = rownames(binarypnfj2[,c(-1,-17,-18)]), speciesnames = colnames(binarypnfj2[,c(-1,-17,-18)]),
  binary = TRUE)

metacom::Imagine(binaryA[,c(-1,-13,-14,-15,-16,-17,-18)], col = c(0, 1), order = TRUE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = 2, xline = 2,
  sitenames = rownames(binaryA[,c(-1,-13,-14,-15,-16,-17,-18)]), speciesnames = colnames(binaryA[,c(-1,-13,-14,-15,-16,-17,-18)]),
  binary = TRUE)

plot(metacom::Imagine(binaryB[,c(-1,-17,-18)], col = c(0, 1), order = TRUE, scores = 1, fill = TRUE,
  xlab = "Species", ylab = "Site", yline = "2", xline = 2,
  sitenames = "", speciesnames = colnames(binaryB[,c(-1,-17,-18)]),
  binary = TRUE))


```

Diversity Indices
```{r}
library(vegan)

pnfjdiverse<-pnfj
pnfjdiverse[is.na(pnfj)]<-0
pnfjdiverse$shannon<-diversity(pnfjdiverse[,c(-1,-17,-18)], index= "shannon")
pnfjdiverse$invsimpson<-diversity(pnfjdiverse[,c(-1,-17,-18, -19)], index= "invsimpson")
pnfjdiverse$simpson<-diversity(pnfjdiverse[,c(-1,-17,-18, -19, -20)], index= "simpson")

pnfjdiverse$tree<-str_extract(pnfjdiverse$site, "[A-Z][:digit:]")

head(pnfjdiverse)


```


load libraries, load data, and project to usable lat/lon
```{r}
library(ggplot2);library(viridis);library(maps);library(mapdata);library(raster);library(proj4); library(ggmap)

mapdata<-read.csv("PNFJ species and coordinates.csv")
mapdata2<-mapdata[,-8:-10]
head(mapdata2)

mapdata3<-subset(mapdata2, Lat == "" )
length(mapdata2$Lat)
length(mapdata3$Lat)

proj4string <- "+proj=utm +zone=19J +south +ellps=WGS84 +datum=WGS84 +units=m +no_defs "

# Source data
xy <- data.frame(mapdata[,2:3])

# Transformed data
pj <- project(xy, proj4string, inverse=TRUE)
latlon <- data.frame(lat=pj$y, lon=pj$x)
head(latlon)

newdata<-latlon
newdata$site<-mapdata$Site
head(newdata)
```

Create patch-level metacom pattern dataset with patch-center lat/lon points
```{r}
library(stringr); library(plyr)
newdata$patch<-str_extract(newdata$site, "[aA-zZ]+")

patchcenter<-ddply(newdata, "patch", summarise,
                   lat = mean(lat),
                   lon   = mean(lon))
patchcenter$pattern<-c("Gleasonian", 
                       "Quasi-Clementsian", 
                       "Gleasonian", 
                       "Gleasonian", 
                       "Clementsian", 
                       "Quasi -Random species loss", 
                       "Gleasonian", 
                       "Quasi-Clementsian", 
                       "Quasi -Clumped species loss", 
                       "Quasi-Clementsian", 
                       "Clementsian", 
                       "Random species loss", 
                       "Gleasonian", 
                       "Quasi-Clementsian", 
                       "Quasi -Clumped species loss", 
                       "Clementsian", 
                       "Gleasonian", 
                       "Quasi -Clumped species loss", 
                       "Quasi-Clementsian", 
                       "Quasi-Clementsian")
patchcenter

```

Add aspect, dbh, canopy cover
```{r}
pnfjenviro<-pnfjdiverse
pnfjenviro$aspect[pnfjenviro$patch == "A"]<-240
pnfjenviro$aspect[pnfjenviro$patch == "B"]<-233
pnfjenviro$aspect[pnfjenviro$patch == "C"]<-178
pnfjenviro$aspect[pnfjenviro$patch == "D"]<-253
pnfjenviro$aspect[pnfjenviro$patch == "E"]<-104
pnfjenviro$aspect[pnfjenviro$patch == "F"]<-251
pnfjenviro$aspect[pnfjenviro$patch == "G"]<-277
pnfjenviro$aspect[pnfjenviro$patch == "H"]<-279
pnfjenviro$aspect[pnfjenviro$patch == "I"]<-220
pnfjenviro$aspect[pnfjenviro$patch == "J"]<-274
pnfjenviro$aspect[pnfjenviro$patch == "K"]<-254
pnfjenviro$aspect[pnfjenviro$patch == "L"]<-253
pnfjenviro$aspect[pnfjenviro$patch == "M"]<-188
pnfjenviro$aspect[pnfjenviro$patch == "N"]<-200
pnfjenviro$aspect[pnfjenviro$patch == "O"]<-212
pnfjenviro$aspect[pnfjenviro$patch == "P"]<-188
pnfjenviro$aspect[pnfjenviro$patch == "Q"]<-184
pnfjenviro$aspect[pnfjenviro$patch == "R"]<-252
pnfjenviro$aspect[pnfjenviro$patch == "S"]<-218
pnfjenviro$aspect[pnfjenviro$patch == "T"]<-253
pnfjenviro$aspect

head(pnfjenviro)
envirodata<-read.csv("group_meansfinalwenviro.csv", row.names= 1,sep =",")
envirodata
envirodata2<-envirodata[,c(1,19, 21)]
head(envirodata2)

envirofinal<-full_join(envirodata2,pnfjenviro, by = "site")
envirofinal$tree<-pnfjdiverse$tree
head(envirofinal)

covermod<-aov(lm(cover~aspect+patch+dbh, data=envirofinal))
anova(covermod)
coverpatchmod<-aov(lm(cover~patch, data =envirofinal))
TukeyHSD(coverpatchmod)

coverdbhmod<-lm(cover~dbh, data=envirofinal)
summary(coverdbhmod)

summary(covermod)

anova(aov(dbh~patch, data =envirofinal))
anova(aov(cover~patch, data =envirofinal))


patterndata<-full_join(envirofinal, patchcenter[c(1,4)], by = "patch")
indlatlon<-newdata
names(indlatlon)[3]<-"tree"
head(indlatlon)
indlatlon[,-4]

patterndata<-full_join(patterndata, indlatlon[,-4], by ="tree")
patterndata<-subset(patterndata, site != "NA")

summary(lm(dbh~patch, data =envirofinal))

#############this has all the data together
head(patterndata)
```

Stats and Data Plots
```{r}

############metacomm structure and variables######################
dbhstructurebox<-ggplot(data=patterndata, aes(pattern, dbh)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("DBH")

dbhstructurebox

pdf("plots/dbhstructure.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(dbhstructurebox)
dev.off()


dbhbypatternmod<-aov(dbh~pattern, data = patterndata)
anova(dbhbypatternmod)
TukeyHSD(dbhbypatternmod)
#quasi-random species loss sig diff from gleasonian p = 0.02

coverstructurebox<-ggplot(data=patterndata, aes(pattern, cover)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("Cover")

coverstructurebox

pdf("plots/coverstructure.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(coverstructurebox)
dev.off()

coverbypatternmod<-aov(cover~pattern, data = patterndata)
anova(coverbypatternmod)
TukeyHSD(coverbypatternmod)
#quasi-random loss x clementsian p = 0.001, quasi -clumped loss x gleasonian p = 0.03, quasi-random x gleasonian p <0.001,
#quasi random loss x quasi clementsian p = 0.003

latstructurebox<-ggplot(data=patterndata, aes(pattern, lat)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("Latitude")

latstructurebox

pdf("plots/latstructure.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(latstructurebox)
dev.off()

latbypatternmod<-aov(lat~pattern, data = patterndata)
anova(latbypatternmod)
TukeyHSD(latbypatternmod)
#quasi clumped loss x gleasonian p <0.001, quasi clumped lossx quasi clementsian p = 0.03, quasi random loss x quasi clumped loss p = 0.01


lonstructurebox<-ggplot(data=patterndata, aes(pattern, lon)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("Longitude")

lonstructurebox

pdf("plots/lonstructure.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(lonstructurebox)
dev.off()

lonbypatternmod<-aov(pattern~lon, data = patterndata)
anova(lonbypatternmod)
TukeyHSD(lonbypatternmod)


##################################diversity##################################
shannonpatchbox<-ggplot(data=patterndata, aes(patch, shannon)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("Shannon Diversity")

shannonpatchbox

pdf("plots/shannonpatch.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannonpatchbox)
dev.off()

shannonbypatchmod<-aov(shannon~patch, data = patterndata)
anova(shannonbypatchmod) #p = 0.037
TukeyHSD(shannonbypatchmod)
#R-N p = 0.05, R-K p = 0.05



shannonstructurebox<-ggplot(data=patterndata, aes(pattern, shannon)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("")+
  ylab("Shannon Diversity")

shannonstructurebox

pdf("plots/shannonstructure.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannonstructurebox)
dev.off()

shannonbypatternmod<-aov(shannon~pattern, data = patterndata)
anova(shannonbypatternmod)
#NS



lonshannonplot<-ggplot(data=patterndata, aes(lon, shannon)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("lon")+
  ylab("Shannon")

lonshannonplot

pdf("plots/shannonlon.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(lonshannonplot)
dev.off()

anova(aov(shannon~lon, data=patterndata))
#NS

latshannonplot<-ggplot(data=patterndata, aes(shannon, lat)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Shannon")+
  ylab("lat")

latshannonplot

pdf("plots/shannonlat.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(latshannonplot)
dev.off()

anova(aov(shannon~lat, data=patterndata))
#MS

latshannonhigh<-ggplot(data=subset(patterndata, height == "H"), aes(shannon, lat)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Shannon")+
  ylab("lat")

latshannonhigh

pdf("plots/shannonathigh.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(latshannonhigh)
dev.off()

latshannonlow<-ggplot(data=subset(patterndata, height == "L"), aes(shannon, lat)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Shannon")+
  ylab("lat")

latshannonlow

pdf("plots/shannonatlow.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(latshannonlow)
dev.off()

anova(aov(shannon~lat, data= subset(patterndata, height == "H")))
anova(aov(shannon~lat, data= subset(patterndata, height == "L")))
#both NS

lonshannonhigh<-ggplot(data=subset(patterndata, height == "H"), aes(shannon, lon)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Shannon")+
  ylab("lon")

lonshannonhigh

pdf("plots/shannonlonhigh.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(lonshannonhigh)
dev.off()

lonshannonlow<-ggplot(data=subset(patterndata, height == "L"), aes(shannon, lon)) +
  geom_point(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Shannon")+
  ylab("lon")

lonshannonlow

pdf("plots/shannonlonlow.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(lonshannonlow)
dev.off()

anova(aov(shannon~lon, data= subset(patterndata, height == "H")))
anova(aov(shannon~lon, data= subset(patterndata, height == "L")))
#both NS


shannonheightbox<-ggplot(data=patterndata, aes(height, shannon)) +
  geom_boxplot(outlier.shape = NA, fill = "lightblue")+
  geom_jitter(height = 0, width = .3)+
  theme_bw()+
  theme(#axis.title.x = element_blank(),
    #axis.title.y = element_blank(),
    axis.text.x  = element_text(angle=90, vjust=0.5, size=12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank())+
  xlab("Height")+
  ylab("Shannon Diversity")

shannonheightbox

pdf("plots/shannonheightbox.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannonheightbox)
dev.off()

diversityheightmod<-aov(shannon~height, data = patterndata)
anova(diversityheightmod)
#NS

diversitycovermod<-aov(shannon~cover, data = patterndata)
anova(diversitycovermod)
#NS

diversitydbhmod<-aov(shannon~dbh, data = patterndata)
anova(diversitydbhmod)
# p = 0.004



#controlling for patch, lon and lat ARE sig....but that autocorrelates w patch
anova(aov(shannon~patch+lon+lat, data= patterndata))




```


Make initial Maps
```{r}
googlemap<-get_googlemap(center=c(lon= -71.68337, lat = -30.660), maptype = "satellite", zoom =14, force = TRUE)

#label patches
pnfjpatchmap<-ggmap(googlemap) + geom_point(data = newdata, mapping = aes(x = lon, y = lat), color = "purple")+
  geom_text(data = patchcenter, aes(label = paste("  ", as.character(patch), sep="")), angle = 60, hjust = 0, color = "yellow")
#remove angle and hjust to center the patch labels

#label all points
pnfjpointmap<-ggmap(googlemap) + geom_point(data = newdata, mapping = aes(x = lon, y = lat), color = "purple")+
  geom_text(data = newdata, aes(label = paste("  ", as.character(site), sep="")), angle = 60, hjust = 0, color = "yellow")

#label metacommunity pattern
pnfjmetacommap<-ggmap(googlemap) + geom_point(data = newdata, mapping = aes(x = lon, y = lat), color = "purple", size =.7)+
  geom_text_repel(data = patchcenter, size = 2, aes(label = paste("  ", as.character(pattern), sep=""), color= pattern),  hjust = 0)
pnfjmetacommap

pdf("plots/patchmap.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(pnfjpatchmap)
dev.off()

pdf("plots/pointmap.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(pnfjpointmap)
dev.off()

pdf("plots/metacommap.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(pnfjmetacommap)
dev.off()

```

Diversity Maps
```{r}

shannonmaphigh<-ggmap(googlemap) + geom_point(data = subset(patterndata, height == "H"), mapping = aes(x = lon, y = lat, color = shannon), size = 0.05) + scale_colour_gradient(low= "yellow", high = "red") 
shannonmaphigh

shannonmaplow<-ggmap(googlemap) + geom_point(data = subset(patterndata, height == "L"), mapping = aes(x = lon, y = lat, color = shannon), size = 0.05) + scale_colour_gradient(low= "yellow", high = "red") 
shannonmaplow

topomap<-get_googlemap(center=c(lon= -71.68337, lat = -30.660), maptype = "terrain", zoom =14, force = TRUE)

shannontopohigh<-ggmap(topomap) + geom_point(data = subset(patterndata, height == "H"), mapping = aes(x = lon, y = lat, color = shannon), size = 0.05) + scale_colour_gradient(low= "yellow", high = "red") 
shannontopohigh

shannontopolow<-ggmap(topomap) + geom_point(data = subset(patterndata, height == "L"), mapping = aes(x = lon, y = lat, color = shannon), size = 0.05) + scale_colour_gradient(low= "yellow", high = "red") 
shannontopolow


pdf("plots/shannonmaphigh.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannonmaphigh)
dev.off()

pdf("plots/shannonmaplow.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannonmaplow)
dev.off()

pdf("plots/shannontopohigh.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannontopohigh)
dev.off()

pdf("plots/shannontopolow.pdf", paper="a4r")
par(omi=c(1,1,1,1))
plot(shannontopolow)
dev.off()
```